Figures

### 2020-05-01 manuscript/figures.Rmd
eq 1 produces geometric depth not calculated depth
describe hu4 in figure caption

![Diagram showing the relations between true (black) and proxy (orange) metrics of lake geometry. Calculated depth from Equation 1 requires a distance and a slope metric.](../figures/slope_diagram_new.pdf){width=75%}

@@

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions. See Equation 1 for a definition of geometric max depth.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```

>>>>

![Diagram showing the relations between true (black) and proxy (orange) metrics of lake geometry. Geometric depth calculated via Equation 1 requires a single distance and slope metric.](../figures/slope_diagram_new.pdf){width=75%}

@@

```{r 02_depth_model_importance, fig.cap = "Importance plot for random forest variables showing increase in mean square error. Higher values indicate greater importance to model predictions. See Equation 1 for a definition of geometric max depth. HUC4 ID is a 'dummy' variable of geographic (hydrologic subbasin) location.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/02_depth_model_importance-1.pdf")
```
